A Study of INC Runs in Sequence

### 2018-12-15 pt_characterization/protocol/intermediate_data/paper.tex
Doc for new runs

\begin{figure}[t]
	\centering
	\subfigure[PT frequency on INC2048 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{2048_sec_pt_hist.eps}
		\label{fig:inc2048}
	}
	\subfigure[PT frequency on INC4096 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{4096_sec_pt_hist.eps}
		\label{fig:inc4096}
	}
	\subfigure[PT frequency on INC8192 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{8192_sec_pt_hist.eps}
		\label{fig:inc8192}
	}
	\subfigure[PT frequency on INC16384 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{16384_sec_pt_hist.eps}
		\label{fig:inc16384}
	}
	\caption{PT Histograms of INC2048 ... INC16384~\label{fig:s9_r2_pt_hist4}}
\end{figure}

\newpage
\section{Decomposition of INC16 Samples}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16 with the first 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_1.eps}
		\label{fig:inc16-1}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_2.eps}
		\label{fig:inc16-2}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_3.eps}
		\label{fig:inc16-3}
	}
	\caption{PT Histograms of INC16-1 ~ INC16-3~\label{fig:inc16_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_4.eps}
		\label{fig:inc16-4}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_5.eps}
		\label{fig:inc16-5}
	}
	\caption{PT Histograms of INC16-4 ~ INC16-5\label{fig:inc16_hist2}}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\subfigure[PT frequency on INC2048 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{2048_sec_pt_hist.eps}
		\label{fig:inc2048}
	}
	\subfigure[PT frequency on INC4096 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{4096_sec_pt_hist.eps}
		\label{fig:inc4096}
	}
	\subfigure[PT frequency on INC8192 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{8192_sec_pt_hist.eps}
		\label{fig:inc8192}
	}
	\subfigure[PT frequency on INC16384 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16384_sec_pt_hist.eps}
		\label{fig:inc16384}
	}
	\caption{PT Histograms of INC2048 ... INC16384~\label{fig:s9_r2_pt_hist4}}
\end{figure}

\clearpage
\section{Decomposition of INC16 Samples}

\begin{figure}[htp!]
	\centering
	\subfigure[PT frequency on INC16 with the first 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_1.eps}
		\label{fig:inc16-1}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_2.eps}
		\label{fig:inc16-2}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_3.eps}
		\label{fig:inc16-3}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_4.eps}
		\label{fig:inc16-4}
	}
	\caption{PT Histograms of INC16-1$~$INC16-4~\label{fig:inc16_hist1}}
\end{figure}

\begin{figure}[H]
	\centering
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_5.eps}
		\label{fig:inc16-5}
	}
	\caption{PT Histograms of INC16-5\label{fig:inc16_hist2}}
\end{figure}
